\documentclass[onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{tikz}
\usetikzlibrary{shapes, arrows, positioning}
\usepackage{float}
\usepackage{booktabs}
\usepackage[center]{caption}
\usepackage{xcolor}

\title{A multimodal evaluation model for improving pedagogical outcomes}

\author{
    \IEEEauthorblockN{Shafiqul Islam} \\
    \IEEEauthorblockA{
        \textit{Begum Rokeya University,Rangpur} \\
    }
}

% Add these to your preamble for figures and tables


\begin{document}

\maketitle

\begin{abstract}
Teacher performance evaluation is a cornerstone of educational quality assurance. Traditionally, student feedback has been the primary tool for assessing teaching effectiveness, but it is often subjective and limited in scope. This proposal outlines a comparative study between a novel multimodal system—which objectively analyzes classroom interactions—and conventional student feedback. The study aims to determine the reliability, validity, and impact of both approaches.
\end{abstract}

\begin{IEEEkeywords}
Teacher evaluation, multimodal system, student feedback, educational assessment, comparative study
\end{IEEEkeywords}

\input{sections/introduction.tex}
\input{sections/related_work.tex}
\input{sections/methodology.tex}
\input{sections/experimental_setup.tex}
\input{sections/system_architecture.tex}


\section{Results and Discussion}
Present the findings of the comparative study here. Include quantitative and qualitative results, statistical analyses, and a discussion interpreting the significance of the results in the context of existing literature.

\section{Conclusion and Future Work}
Summarize the main contributions and findings of the study. Discuss limitations and propose directions for future research.

\section*{Acknowledgment}
(Optional) Acknowledge any funding sources, institutional support, or individuals who contributed to the research but are not listed as authors.

\bibliographystyle{IEEEtran}
\bibliography{research}

\end{document}