% Import title page (commented out - file not found)
% \input{titlepage}

\thispagestyle{empty}
\vspace*{1cm}

\begin{center}
    {\Large\bfseries DECLARATION}
\end{center}

\vspace{0.8cm}

I, \textbf{\theauthor}, student of Bachelor of Science in Computer Science and Engineering, ID: 1905017, hereby declare that this thesis entitled \textbf{``\projectTitle''} is a record of original work done by me under the supervision of \textbf{\thesupervisortitle~\thesupervisor}, Department of Computer Science and Engineering, Begum Rokeya University, Rangpur.

\vspace{0.8cm}

I further declare that this work has not been submitted elsewhere for any degree or diploma. The contents of this thesis are based on my own research work and the sources of information have been duly acknowledged.

\vspace{2cm}

\begin{flushright}
    \textbf{\theauthor}\\
    Student ID: 1905017\\
    Department of Computer Science and Engineering\\
    Begum Rokeya University, Rangpur\\
    \today
\end{flushright}

\clearpage

% Approval page
\chapter*{Approval}
\thispagestyle{empty}
This is to certify that the thesis entitled ``\projectTitle'' submitted by \theauthor\ (ID: 1905028) has been accepted as satisfactory in partial fulfillment of the requirements for the degree of \thedegree\ in \themajor.

\vspace{3cm}
\noindent
\rule{7cm}{0.5pt}\\
\thesupervisor\\
\thesupervisortitle\\
\thedepartment\\
\theuniversity


% Dedication
\newpage
\thispagestyle{empty}
\vspace*{3cm}

\begin{center}
    {\Large \textbf{Dedication}}

    \vspace{2cm}

    \begin{minipage}{0.8\textwidth}
    \large
    \textit{To my beloved parents,}

    \vspace{0.5cm}

    whose unwavering love, endless support, and countless sacrifices have made all my achievements possible. Your belief in me has been my greatest strength throughout this journey.

    \vspace{0.5cm}

    \textit{And to all dreamers who dare to innovate.}
    \end{minipage}
\end{center}
\clearpage

% Acknowledgments
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
I would like to express my sincere gratitude to my supervisor, \thesupervisor, for his invaluable guidance, continuous support, and encouragement throughout this research work. His expertise and insights have been instrumental in shaping this thesis.

I am also grateful to the Department of Computer Science and Engineering at Begum Rokeya University, Rangpur, for providing the resources and environment conducive to research. Special thanks to my fellow researchers and the open-source community for their contributions and support.

\clearpage