% This is now Chapter 4
This section describes the environment, tools, and procedures used to conduct the comparative study between the multimodal teacher evaluation system and traditional student feedback.

\subsection{Classroom Environment}
Experiments were conducted in real university classrooms across three academic departments (STEM, Humanities, Social Sciences). Each classroom was equipped with standard teaching facilities and additional sensors for multimodal data collection.

\subsection{Hardware and Software}
\begin{itemize}
    \item \textbf{Audio:} Directional microphones (Shure MX391) placed at the front and rear of the classroom.
    \item \textbf{Video:} Two wide-angle HD cameras (Logitech C920) positioned to capture both teacher and student interactions.
    \item \textbf{Computing:} A dedicated workstation (Intel i7, 32GB RAM, NVIDIA RTX 3060) for real-time data processing and storage.
    \item \textbf{Software:} 
        \begin{itemize}
            \item PRAAT for audio feature extraction
            \item OpenPose/HRNet for pose estimation
            \item Python (NumPy, pandas, scikit-learn) for data analysis
            \item Custom NLP pipeline for discourse analysis
        \end{itemize}
\end{itemize}

\begin{table}[H]
    \centering
    \normalsize
    \caption{Summary of Collected Dataset}
    \label{tab:dataset_summary}
    \begin{tabular}{lcc}
        \toprule
        \textbf{Data Type} & \textbf{Sessions} & \textbf{Total Size} \\
        \midrule
        Audio & 90 & 18 hours (12 GB) \\
        Video & 90 & 18 hours (90 GB) \\
        Transcripts & 90 & 1.2M words (8 MB) \\
        Student Feedback & 90 & 1,350 responses (0.5 MB) \\
        \bottomrule
    \end{tabular}
\end{table}


\subsection{Data Collection Procedure}
\begin{enumerate}
    \item \textbf{Session Preparation:} Instructors and students were briefed and consent was obtained. Equipment was set up before each session.
    \item \textbf{Recording:} Each teaching session (50 minutes) was recorded for both audio and video. Student feedback was collected immediately after each session via online forms.
    \item \textbf{Synchronization:} All data streams were time-synchronized using a central clock to ensure accurate multimodal analysis.
    \item \textbf{Data Storage:} Raw data was securely stored on encrypted local drives. Only anonymized data was used for analysis.
\end{enumerate}

\subsection{Dataset Overview}
A total of 90 teaching sessions were recorded (30 instructors × 3 sessions each). For each session, the following data was collected:
\begin{itemize}
    \item Audio recordings (WAV, 44.1kHz)
    \item Video recordings (MP4, 1080p)
    \item Automatic transcripts (TXT)
    \item Student feedback responses (CSV)
\end{itemize}

